Demes: a standard format for demographic models

### 2022-08-08 paper.tex
added author and software for MSMC

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Ryan N. Gutenkunst}
\author[4]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[3]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California at Irvine}

@@

\section*{Acknowledgments}
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst was supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher is supported by the Robertson Foundation.

>>>>

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Ryan N. Gutenkunst}
\author[4]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[3]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California, Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

\section*{Acknowledgments}
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst was supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher is supported by the Robertson Foundation.
Stephan Schiffels was supported by funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No 851511).
